EldersAIR Med Visit Summary

### 2021-05-06 manuscript_tables_figures.Rmd
New RMDs for PM and Health paper results

>>>>

```{r}
kw_filtertype_data <- elders_cleaned_dataset_by_visit %>% 
  select(area, home, adult_id_char, winter_id, sampling_visit, treatment,
         filter_type, kw_perc_expected) %>% 
  mutate(treatment_filter_type = as.character(treatment),
         filter_type = as.character(filter_type),
         treatment_filter_type2 = if_else(treatment_filter_type == "Filter", filter_type,
                                         treatment_filter_type),
         treatment_filter_type = as.factor(treatment_filter_type2),
         filter_type = as.factor(filter_type)) %>% 
  select(-treatment_filter_type2) 
  group_by(treatment) %>% 
  summarize(mean(kw_perc_expected, na.rm = T), median(kw_perc_expected, na.rm = T))
kw_filtertype_data

summary(kw_filtertype_data)

compliance_summary <- elders_cleaned_dataset_by_visit %>% 
  filter(winter_id == 2) %>% 
  distinct(area, home, .keep_all = T) %>% 
  filter(treatment == "Filter") %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "25Q KW % Exp" = quantile(kw_perc_expected, 0.25),
            "Med KW % Exp" = median(kw_perc_expected),
            "75Q KW % Exp" = quantile(kw_perc_expected, 0.75),
            "Max KW % Exp" = max(kw_perc_expected))
compliance_summary
```

### 2021-05-06 medvisit_summary.Rmd
New RMDs for PM and Health paper results

---
title: "EldersAIR Med Visit Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 1 April 2021"
output: pdf_document
---

@@

# Cardiovascular outcomes from Med visit
```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, outcome)) + 
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, outcome)) + 
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(outcome)) + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(outcome)) + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

# Spirometry outcomes from Med visit
```{r, fig.height=6, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=6, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T),
         var = as.factor(var)) %>% 
  ungroup() %>% 
  ggplot() + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T),
         var = as.factor(var)) %>% 
  ungroup() %>% 
  ggplot() + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

>>>>

---
title: "EldersAIR Med Visit Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 3 May 2021"
output: pdf_document
---

@@

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, outcome)) + 
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, outcome)) + 
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(outcome)) + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  select(area, treatment_blind, sp02, pr, bp_sys, bp_dia, hr, age, height_inches,
         weight_lbs, bmi, adult_id_char) %>% 
  pivot_longer(cols = c("sp02":"bmi"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(outcome)) + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=6, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=6, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_blind, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T),
         var = as.factor(var)) %>% 
  ungroup() %>% 
  ggplot() + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 1") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r, fig.height=8.5, fig.width=8.5, eval = FALSE}
medvisit_plot <- analysis_data %>% 
  filter(winter_id == 2) %>% 
  filter(spiro_status == "Acceptable") %>% 
  select(area, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp,
         treatment_blind, adult_id_char) %>% 
  pivot_longer(cols = c("fvc":"fev1_pp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  arrange(area, adult_id_char, var) %>% 
  group_by(area, adult_id_char, var) %>% 
  mutate(outcome = mean(value, na.rm = T),
         var = as.factor(var)) %>% 
  ungroup() %>% 
  ggplot() + 
    geom_histogram(aes(outcome), colour = "black") +
    labs(title = "Winter 2") +
    theme_minimal() +
    theme(plot.title = element_text(size = 18, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 45, vjust = 0.5),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free")
medvisit_plot
```

```{r}
# Summarize data for Paul to review

# Load data

health_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) %>% 
  select(area, home, adult_id_char, winter_id, sampling_visit, sp02:spiro_result) %>% 
  arrange(area, adult_id_char, winter_id, sampling_visit) %>% 
  rename(sp02_pulse_rate = pr,
         systolic_bp = bp_sys,
         diastolic_bp = bp_dia,
         heart_rate_bp = hr,
         sex = gender,
         fvc_percent_predicted = fvc_pp,
         fev1_percent_predicted = fev1_pp,
         fev1_fvc_ratio_percent_predicted = fev1_fvc_ratio_pp)

write_csv(health_data, paste0(file_path, "Output/eldersair_health_data.csv"), na = "")
```

```{r}
health_summary_function <- function(data, var, var_label) {

  health_summary <- data %>% 
   rename(new_var = var) %>% 
   filter(!is.na(new_var)) %>% 
   summarize("Mean" = round(mean(new_var), digits = 1),
             "Std Dev" = round(sd(new_var), digits = 1),
             "# Observations" = n(),
             "Min" = round(min(new_var), digits = 1),
             "Median" = round(median(new_var), digits = 1),
             "Max" = round(max(new_var), digits = 1))  %>% 
   mutate("Health Metric" = var_label) %>% 
   select(`Health Metric`, Mean:Max) 
kable(health_summary)

acceptable_function <- function(data, var, var_label) {

  health_summary <- data %>% 
   filter(spiro_status == "Acceptable") %>% 
   rename(new_var = var) %>% 
   filter(!is.na(new_var)) %>% 
   summarize("Mean" = round(mean(new_var), digits = 1),
             "Std Dev" = round(sd(new_var), digits = 1),
             "# Observations" = n(),
             "Min" = round(min(new_var), digits = 1),
             "Median" = round(median(new_var), digits = 1),
             "Max" = round(max(new_var), digits = 1))  %>% 
   mutate("Health Metric" = var_label) %>% 
   select(`Health Metric`, Mean:Max) 
kable(health_summary)

}
```

```{r}
health_summary_function(health_data, "sp02", "SPO2")
```
Minimum SPO2 (and other low values) are likely bad readings from user error or 
instrument malfunction. Do we sensor these values in the analysis or leave as-is?  
\linebreak
\linebreak

```{r}
health_summary_function(health_data, "sp02_pulse_rate", "Pulse rate - from SPO2")
```
\linebreak

```{r}
health_summary_function(health_data, "systolic_bp", "Systolic BP")
```
\linebreak

```{r}
health_summary_function(health_data, "diastolic_bp", "Diastolic BP")
```
Do we sensor very low and unrealistic values such as Diastolic BP of 20mmHg?  
\linebreak

```{r}
health_summary_function(health_data, "heart_rate_bp", "Heart rate - from BP")
```
\linebreak

```{r}
health_summary_function(health_data, "fvc", "FVC")
acceptable_function(health_data, "fvc", "FVC - Acceptable")
```
For all Spirometry outcomes, should we use only the sessions marked as "Acceptable"?  
\linebreak
\linebreak

```{r}
health_summary_function(health_data, "fev1", "FEV1")
acceptable_function(health_data, "fev1", "FEV1 - Acceptable")
```
\linebreak

```{r}
health_summary_function(health_data, "fev1_fvc_ratio", "FEV1/FVC Ratio")
acceptable_function(health_data, "fev1_fvc_ratio", "FEV1/FVC Ratio - Acceptable")
```
\linebreak

```{r}
health_summary_function(health_data, "fvc_percent_predicted", "FVC Percent Predicted")
acceptable_function(health_data, "fvc_percent_predicted", "FVC Percent Predicted - Acceptable")
```
How accurate are the percept predicted values?  
What metrics are used to calculate percent predicted? Age and height? Also race/ethnicity?  
Should percent predicted values be used as a primary outcome in the publications?  
\linebreak
\linebreak

```{r}
health_summary_function(health_data, "fev1_percent_predicted", "FEV1 Percent Predicted")
acceptable_function(health_data, "fev1_percent_predicted", "FEV1 Percent Predicted - Acceptable")
```
